%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Marshall Moutenot
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Marshall Moutenot}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

	mobile: 615 519 7142
	\vspace{0mm}\\\vspace{0mm}%
	email: mmoutenot@gmail.com
	\vspace{0mm}\\\vspace{0mm}%
	github: http://github.com/mmoutenot
	\vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Machine learning, computer security, visualization and graph theory.

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Tufts University School of Engineering}, Medford, Massachusetts \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Science in Computer Science} \hfill \textbf{ September 2009 - 2013 (Expected)}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Deans List: All Semesters
        \item Advisors:  Professor Norman Ramsey
    \end{list2}\vspace{-1.5mm}
    
    %__________________________________________________________________________________________________________________
    % Honours and Awards
    %\section{\mysidestyle Honours and\\Awards} 

    %Best Paper Award, Griffith School of Engineering Research Conference, Nathan, 2007              \vspace{1mm}\\%



    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Relevant Coursework}
		Machine Structure and Assembly (also TA), Web Programming, Machine Learning, Programming Language (Functional Programming), Data Structures, Algorithms

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    
    % \textbf{Mozilla}, Mountain View, CA \vspace{2mm}\\\vspace{1mm}%
    %\textsl{Security Intern} \hfill \textbf{May -- September 2012}\\
    
 \textbf{Microsoft}, Seattle, WA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bing Security SDET Intern} \hfill \textbf{May -- September 2011}\\
    Created an IDN to detect potential phishing URLs registered by third parties.
    Developed competitive automated security testing tools to detect vulnerabilities (XSS, open redirect, null byte injection, etc). C\# development with SQL backend. High level reporting and web user interface (AJAX, HTML5, ASP.NET).    
    
    \textbf{Redstar Ventures}, Cambridge, Massachusetts \vspace{2mm}\\\vspace{1mm}%
    \textsl{Developer} \hfill \textbf{January 2012 - present}\\
	Developing website in Django environment with small team.
	
    \textbf{Tufts University}, Medford, Massachusetts \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{2010-2011}\\
    Undergraduate courses in Machine Structure/Assembly Language, and Data Structures. Including helping with large-scale projects in C and general unix tutorial. Taught classes on VIM.

    \textbf{Emma, Inc.}, Nashville, TN \vspace{2mm}\\\vspace{1mm}%
    \textsl{Systems/Security Intern} \hfill \textbf{Summers, 2010, 2009, 2007}\vspace{1.5mm}\\\vspace{0mm}%
	Nessus security scans, Nmap network scans, SQL injection. Automated security scan (nessus/nmap) and report generation with cron jobs and Apache web framework. Shell and Bash script programming, server installation, network analysis. Created a visual representation of consumer location and density using Google Maps API, PHP, and PostresSQL.
	
	\textbf{University School of Nashville Computer Courses}, Nashville, TN \vspace{2mm}\\\vspace{1mm}%
    \textsl{Founder, Head Instructor} \hfill \textbf{2007-2010}\vspace{1.5mm}\\\vspace{0mm}%
	Initiated computer education for rising 5th through 9th graders. Lead teacher in Flash, Photoshop, Web Design, Lego Robotics, Programming (with Robocode and Python), Alice, and Film classes. Managed employees, business assets, advertising, and customer relations. Developed a profitable small business that is now in its 5th year.


    %__________________________________________________________________________________________________________________
    % Computer Skills
	\section{\mysidestyle Computer Skills}
	Python, C(++$\|\#$), Django, Bash, SQL, Vim, Linux User, Android, Javascript/JQuery, ASP.NET
    
    \section{\mysidestyle Activities} 

    Defcon/B-Sides Attendee (2011),
	Unix Systems Administrator (2009 - Present),
	WMFO Exec Board – Ops Director (2009 - 2011),
	Private Pilot Training (2010 - Present),
	DJ and Turntablist (2005 -Present),
	TRUNK! Children's Theatre (2010 - Present),

    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
%\section{\mysidestyle Referees} 

%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

